TwinPeaks2018

### 2018-05-24 doc/ms.tex
The change of variables
Do it with differentiation

The KL divergence from $p_{\rm NS}$ to a constrained distribution
$p(x; x^*) = \pi(x)\mathds{1}(x > x^*)/X(x^*)$ is
\begin{align}
D_{\rm KL}\left(p(x; x^*) \,||\, p_{\rm NS}\right)
    &= \int p(x; x^*)
            \log \left[\frac{p_{\rm NS}}{p_{\rm NS}}\right] \, dx \\
    &= \int \pi(x)\mathds{1}(x > x^*)/X(x^*)
            \log \left[\frac{\pi(x)\mathds{1}(x > x^*)/X(x^*)}
                            {\frac{\pi(x)}{C X(x)}}\right] \, dx \\
    &= \int \pi(x)\mathds{1}(x > x^*)/X(x^*)
            \log \left[\frac{\pi(x)\mathds{1}(x > x^*)/X(x^*)}
                            {\frac{\pi(x)}{C X(x)}}\right] \, dx \\
    &= \log C + \int_{x^*}^{\infty} \frac{\pi(x)}{X(x^*)}
            \log \left[\frac{X(x)}{X(x^*)}\right] \, dx
\end{align}

Do a change of variables to make $X$ the integrand. Its prior is uniform
because $X$ is a cumulative probability.

>>>>

The KL divergence from $p_{\rm NS}$ to a constrained distribution
$p(x; x^*) = \pi(x)\mathds{1}(x > x^*)/X(x^*)$ is
\begin{align}
D_{\rm KL}\left(p(x; x^*) \,||\, p_{\rm NS}\right)
    &= \int p(x; x^*)
            \log \left[\frac{p_{\rm NS}}{p_{\rm NS}}\right] \, dx \\
    &= \int \pi(x)\mathds{1}(x > x^*)/X(x^*)
            \log \left[\frac{\pi(x)\mathds{1}(x > x^*)/X(x^*)}
                            {\frac{\pi(x)}{C X(x)}}\right] \, dx \\
    &= \int \pi(x)\mathds{1}(x > x^*)/X(x^*)
            \log \left[\frac{\pi(x)\mathds{1}(x > x^*)/X(x^*)}
                            {\frac{\pi(x)}{C X(x)}}\right] \, dx \\
    &= \log C + \int_{x^*}^{\infty} \frac{\pi(x)}{X(x^*)}
            \log \left[\frac{X(x)}{X(x^*)}\right] \, dx.
\end{align}

Let's see how this varies as you change the thresholded distribution
by varying $x^*$:
\begin{align}
\frac{d}{dx^*} D_{\rm KL}\left(p(x; x^*) \,||\, p_{\rm NS}\right)
    &= \frac{d}{dx^*} \log C +
        \frac{d}{dx^*}\int_{x^*}^{\infty} \frac{\pi(x)}{X(x^*)}
            \log \left[\frac{X(x)}{X(x^*)}\right] \, dx \\
    &= \frac{d}{dx^*}\int_{x^*}^{\infty} \frac{\pi(x)}{X(x^*)}
            \log \left[\frac{X(x)}{X(x^*)}\right] \, dx \\
    &= \frac{\pi(x^*)}{X(x^*)}
            \log \left[\frac{X(x^*)}{X(x^*)}\right] \, dx \\
    &= 0.
\end{align}
That is, it doesn't change! The KL divergence
{\em from the distribution actually sampled} to
{\em any thresholded distribution} is the same!
